%----------------------------------------------------------------------------------------
% SINGLE COLUMN RESUME - Ganesh Singha
%----------------------------------------------------------------------------------------
\documentclass[10pt, a4paper]{article}

\usepackage[top=0.42in, bottom=0.42in, left=0.6in, right=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{array}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\definecolor{primary}{RGB}{30, 64, 175}
\definecolor{lightgray}{RGB}{243, 244, 246}
\definecolor{darkgray}{RGB}{55, 65, 81}

\hypersetup{
  colorlinks=true,
  urlcolor=primary,
  linkcolor=primary
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Section formatting
\titleformat{\section}
  {\large\bfseries\color{primary}}
  {}{0em}{}
  [\color{primary}\titlerule]
\titlespacing{\section}{0pt}{6pt}{3pt}

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

\newcommand{\projectEntry}[4]{
  \textbf{#1} \hfill \textit{\small #2} \\
  \small\textit{Technologies: #3} \\
  \small #4 \vspace{4pt}
}

\begin{document}

%----------------------------------------------------------------------------------------
% HEADER
%----------------------------------------------------------------------------------------
\begin{center}
  {\Huge\bfseries Ganesh Singha} \\[4pt]
  \small
  \faPhone\ +91 9144070952 \quad
  \faEnvelope\ \href{mailto:ganeshsingha741@gmail.com}{ganeshsingha741@gmail.com} \quad
  \faGithub\ \href{https://github.com/singhaganesh}{github.com/singhaganesh} \quad
  \faLinkedin\ \href{https://www.linkedin.com/in/ganesh-singha/}{linkedin.com/in/ganesh-singha}
\end{center}

\vspace{2pt}
\hrule height 1.5pt
\vspace{6pt}

%----------------------------------------------------------------------------------------
% CAREER OBJECTIVE
%----------------------------------------------------------------------------------------
\section{Career Objective}
Results-driven Computer Science postgraduate student at Brainware University (MCA, CGPA: 8.97) with hands-on experience building full-stack applications using Java, Spring Boot, and modern web and mobile technologies. Proven ability to deliver production-grade systems --- including a patented EV charging platform and an AI-powered IoT chatbot --- across backend, Android, and React ecosystems. Currently working as a Junior Engineer at SEPLE NovaEdge Pvt. Ltd. while actively expanding expertise in IoT, AI integration, and cloud-based architectures.

%----------------------------------------------------------------------------------------
% TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{tabular}{@{}p{3cm} p{13cm}}
  \textbf{Frontend:}   & React, Next.js, Flutter, Android SDK (Kotlin), HTML/CSS, JavaScript, Redux Toolkit, Material UI, Tailwind CSS \\[2pt]
  \textbf{Backend:}    & Java, Spring Boot, Spring Security, Spring MVC, Hibernate, REST API, Maven, MySQL, PostgreSQL \\[2pt]
  \textbf{DevOps:}     & Git, GitHub, Docker, CI/CD, Firebase, Postman, Maven, AWS \\[2pt]
  \textbf{AI Tools:}   & OpenAI API, Claude Code (Anthropic), CLI \\[2pt]
  \textbf{Tools:}      & IntelliJ IDEA, Android Studio, Visual Studio Code, Antigravity \\
\end{tabular}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\textbf{Brainware University} \hfill \textit{2024 -- Pursuing} \\
Master of Computer Applications \hfill CGPA: 8.97 \\[4pt]
\textbf{MAKAUT} \hfill \textit{2021 -- 2024} \\
Bachelor of Computer Applications \hfill CGPA: 8.43

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Experience}

{\small\textbf{Junior Engineer} $|$ \textit{SEPLE NovaEdge Pvt. Ltd., Kolkata} \hfill \textit{December 2025 -- Present}} \\[2pt]
{\small Collaborated within a three-member engineering team to design and deliver two IoT-based software products on the ThingsBoard PE platform. Built an AI-powered chatbot integrating OpenAI GPT that reduced manual device data querying time by approximately 60\% through natural language automation. Contributed to SWatch360, a Flutter cross-platform mobile application used for real-time IoT device monitoring and control.}

\vspace{4pt}
{\small\textbf{Projects:}}
\begin{itemize}[leftmargin=*, itemsep=1pt, topsep=2pt]
  \item {\small\textbf{ThingsBoard IoT Chatbot} $|$ An AI-powered IoT chatbot integrating ThingsBoard and OpenAI GPT to enable natural language querying of real-time device telemetry and attributes. \href{https://github.com/singhaganesh/ThingsBoard-Bot.git}{\textit{[GitHub]}}}
  \item {\small\textbf{SWatch360 -- IoT Mobile Application} $|$ A Flutter-based cross-platform mobile app built on ThingsBoard PE for real-time IoT device monitoring and control. \href{https://github.com/Itinerant18/SWatch360.git}{\textit{[GitHub]}}}
\end{itemize}

\vspace{6pt}

{\small\textbf{Java Full Stack Intern} $|$ \textit{Ardent Computech Pvt. Ltd., Kolkata} \hfill \textit{July 2024 -- August 2024}} \\[2pt]
{\small Collaborated in a two-member team to architect and implement a real-time chat web application from the ground up. Owned the Spring Boot backend by creating REST API endpoints and implementing core server-side business logic, accelerating development through reusable service components.}

\vspace{4pt}
{\small\textbf{Projects:}}
\begin{itemize}[leftmargin=*, itemsep=1pt, topsep=2pt]
  \item {\small\textbf{Chat Web Application} $|$ A real-time web-based chat application with Spring Boot backend and WebSocket support for instant messaging between users. \href{https://github.com/singhaganesh/chat-app-web.git}{\textit{[GitHub]}}}
\end{itemize}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}

\textbf{EV Charging Platform} $|$ \textit{Patent No. 202531058380} \hfill \textit{February 2026 -- Present} \\
\small Architected and patented a full-stack EV charging ecosystem that supports Drivers, Station Owners, and Administrators, featuring a Spring Boot REST API backend, a native Kotlin Android app, and a React web dashboard. Enforced real-time slot availability tracking, role-based access control (RBAC), and dynamic pricing models backed by a relational database. Integrated Google Maps API for optimized geospatial station discovery and reduced mobile data load latency. \\
\small\textit{Technologies: Spring Boot, JWT, Kotlin (Android), React, Google Maps API, MySQL, AWS} $|$ \href{https://github.com/singhaganesh/EV-Project.git}{\textit{[GitHub]}}

\vspace{6pt}

\textbf{ThingsBoard IoT Chatbot} \hfill \textit{March 2026 -- Present} \\
\small Engineered an AI-powered IoT chatbot that integrates ThingsBoard with OpenAI GPT to enable natural language querying of real-time device telemetry and attributes. Designed a multi-layered Spring Boot backend with smart context filtering to minimize OpenAI token consumption and 60-second caching to optimize ThingsBoard API calls. Engineered multi-turn conversation memory with MySQL persistence and role-based device scoping via custom X-TB token authentication. \\
\small\textit{Technologies: Spring Boot, OpenAI API, ThingsBoard REST API, JavaScript, MySQL} $|$ \href{https://github.com/singhaganesh/ThingsBoard-Bot.git}{\textit{[GitHub]}}

\vspace{6pt}

\textbf{E-Commerce Platform} \hfill \textit{January 2026 -- Present} \\
\small Engineered a multi-role full-stack e-commerce platform supporting Customers, Sellers, and Administrators with a Spring Boot 3 backend and React 19 frontend. Applied JWT-based stateless authentication with Spring Security and role-based access control (RBAC) to secure REST API endpoints. Built a Seller dashboard with multi-step registration, real-time inventory management, order tracking, and sales analytics. Integrated Redux Toolkit for scalable client-side state management and Material UI with Tailwind CSS. \\
\small\textit{Technologies: Spring Boot, JWT, React, Redux Toolkit, PostgreSQL, Tailwind CSS} $|$ \href{https://github.com/singhaganesh/Ecommerce-Web.git}{\textit{[GitHub]}}


%----------------------------------------------------------------------------------------
% CERTIFICATIONS
%----------------------------------------------------------------------------------------
\section{Certifications}
\begin{itemize}[leftmargin=*, itemsep=4pt, topsep=2pt]
  \item \textbf{Claude Code in Action} $|$ Anthropic Academy $|$ \href{https://drive.google.com/file/d/10fWusr3B5y7uqHlejeYHJPfNI7hfHuqM/view?usp=sharing}{\faExternalLinkAlt\ View Certificate} \hfill \textit{March 2026}

  \item \textbf{Software Engineering Job Simulation (Java Spring Boot)} $|$ Hewlett Packard Enterprise $|$ \href{https://drive.google.com/file/d/1hGXeApV5uc2bW2ESBK71V4ilGfFzFotm/view}{\faExternalLinkAlt\ View Certificate} \hfill \textit{May 2025}

  \item \textbf{Core Java} $|$ HackerRank $|$ \href{https://drive.google.com/file/d/13JBQqnl3u7fpQG-NOGJxgJ3rv7yvUtII/view?usp=sharing}{\faExternalLinkAlt\ View Certificate} \hfill \textit{November 2024}
\end{itemize}

%----------------------------------------------------------------------------------------
% ACHIEVEMENTS
%----------------------------------------------------------------------------------------
\section{Achievements}
\begin{itemize}[leftmargin=*, itemsep=4pt, topsep=2pt]
  \item \textbf{1st Place in Binary Battleground 2K25} $|$ Brainware University $|$ \href{https://drive.google.com/file/d/1klUmjWwahrMnXpMx_ync2RBuk1tg8U0F/view?usp=sharing}{\faExternalLinkAlt\ View Certificate} \hfill \textit{February 2025}
\end{itemize}

%----------------------------------------------------------------------------------------
% HACKATHONS & EVENTS
%----------------------------------------------------------------------------------------
\section{Hackathons \& Events}

\textbf{Smart India Hackathon 2025} $|$ \textit{Internal Hackathon Qualifier} $|$ Brainware University \hfill \textit{October 2025} \\[2pt]
\small Qualified for the internal round of Smart India Hackathon 2025 as part of a 6-member team, building a civic issue reporting and management platform for Jharkhand. Solely responsible for designing and developing the entire Spring Boot backend, including REST API architecture, database design, and server-side business logic. \\
\small\textit{Technologies: Spring Boot, MySQL, REST API, HTML/CSS/JavaScript} $|$ \href{https://github.com/singhaganesh/jharkhand-civic-issue.git}{\textit{[GitHub]}}

%----------------------------------------------------------------------------------------
% LANGUAGES & HOBBIES
%----------------------------------------------------------------------------------------
\section{Languages Known}
English, Hindi, Bengali

\section{Hobbies \& Interests}
Riding Bike, Travelling, Solving Rubik's Cube

\end{document}